High Contrast Coronagraphy

### 2025-01-09 src/tex/ms.tex
removed conda-cache

\begin{table}
\caption{Definition of physical quantities}\label{tab1}
\begin{center}
\begin{tabular}{@{}l|l|l|l@{}}
\hline
$i$ & The imaginary unit & $c$ & Speed of light in a vacuum \\\hline
$\vec{E}$ & Electric field & $\vec{H}$ & Magnetic field \\\hline
$\mathcal{D}$ & Displacement field & $\mathcal{B}$ & Magnetizing field \\\hline
$\epsilon$ & Electric permittivity & $\epsilon_0$ & Electric permittivity of vacuum \\\hline
$\mu$ & Magnetic permittivity & $\mu_0$ & Magnetic permittivity of vacuum \\\hline
$\omega$ & Wavenumber & $\vec{k}$ & Wavevector \\\hline
$\lambda$ & Wavelength & $\lambda_0$ & Center wavelength in the bandpass \\\hline
$\Pi$ & The telescope pupil function & $\Delta\lambda$ & The width of the bandpass \\\hline
$D$ & Diameter of the pupil & $n$ & (Complex) refractive index of macroscopic media \\\hline
$\mathcal{F}_{x,y}[\cdot]$ & Fourier transform operator & $\mathcal{F}^{-1}_{x,y}[\cdot]$ & Inverse Fourier transform operator \\\hline
$C_\lambda[\cdot]$ & A general coronagraph propagation operator & $\Psi_\lambda[\vec{k}]$ & Coronagraphic image \\\hline
$\phi$ & The phase of the electric field & $\alpha$ & The amplitude of the electric field \\\hline
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{equation}
\begin{aligned}
\frac{\partial\mathcal{D}}{\partial t} \quad & = \quad \nabla\times\mathcal{H},   & \quad \text{(Faraday's law)} \\[5pt]
\frac{\partial\mathcal{B}}{\partial t} \quad & = \quad -\nabla\times\mathcal{E},  & \quad \text{(Ampere's Law)}   \\[5pt]
\nabla\cdot\mathcal{B}                 \quad & = \quad 0,                         & \quad \text{(Gauss's law)}   \\[5pt]
\nabla\cdot\mathcal{D}                 \quad & = \quad 0.                         & \quad \text{(Coulomb's law)}
\end{aligned}
\end{equation}

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $\mathcal{D}=\epsilon \mathcal{E}$ and $\mathcal{B}=\mu \mathcal{H}$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
\mu \epsilon \frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is it's Fourier transform. A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point. This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.

>>>>

\begin{table}
\caption{Definition of physical quantities}\label{tab1}
\begin{center}
\begin{tabular}{@{}l|l|l|l@{}}
\hline
$i$ & The imaginary unit & $c$ & Speed of light in a vacuum \\\hline
$\vec{E}$ & Electric field & $\vec{H}$ & Magnetizing field \\\hline
$\mathcal{D}$ & Electric Displacement & $\mathcal{B}$ & Magnetic field \\\hline
$\epsilon$ & Electric permittivity & $\epsilon_0$ & Electric permittivity of vacuum \\\hline
$\mu$ & Magnetic permeability & $\mu_0$ & Magnetic permeability of vacuum \\\hline
$\omega$ & Angular frequency & $\vec{k}$ & Wave vector \\\hline
$\lambda$ & Wavelength & $\lambda_0$ & Central wavelength in the bandpass \\\hline
$\Pi$ & The telescope pupil function & $\Delta\lambda$ & The width of the bandpass \\\hline
$D$ & Diameter of the pupil & $n$ & (Complex) refractive index of macroscopic media \\\hline
$\mathcal{F}_{x,y}[\cdot]$ & Fourier transform operator & $\mathcal{F}^{-1}_{x,y}[\cdot]$ & Inverse Fourier transform operator \\\hline
$C_\lambda[\cdot]$ & A general coronagraph propagation operator & $\Psi_\lambda[\vec{k}]$ & Coronagraphic image \\\hline
$\phi$ & The phase of the electric field & $\alpha$ & The amplitude of the electric field \\\hline
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{equation}
\begin{aligned}
\frac{1}{c}\frac{\partial\mathcal{D}}{\partial t} \quad & = \quad \nabla\times\mathcal{H},   & \quad \text{(Faraday's law)} \\[5pt]
\frac{1}{c}\frac{\partial\mathcal{B}}{\partial t} \quad & = \quad -\nabla\times\mathcal{E},  & \quad \text{(Ampere's Law)}   \\[5pt]
\nabla\cdot\mathcal{B}                 \quad & = \quad 0,                         & \quad \text{(Gauss's law)}   \\[5pt]
\nabla\cdot\mathcal{D}                 \quad & = \quad 0.                         & \quad \text{(Coulomb's law)}
\end{aligned}
\end{equation}

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $\mathcal{D}=\epsilon \mathcal{E}$ and $\mathcal{B}=\mu \mathcal{H}$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
\frac{\mu \epsilon}{c^2} \frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with angular frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is its Fourier transform.
%
A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point.
%
This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.
